\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites

### 2017-12-14 paper/newResearchDesign.tex
new abstract

Websites have become a prominent source of data for automated text analysis in political science. However, extant research lacks common standards and often glosses over the details on how such analyses are conducted, exposing itself to potential pitfalls associated with this process and making replication difficult. We develop a set of guidelines and procedures to be followed in order to produce valid results. In order to develop a valid research design, the appropriate selection of cases and URLs is crucial. For the acquisition of website data, we cover several scraping methods and difficulties that can arise in the process. Pre-processing is a common step in text analysis, but when websites are concerned, additional measures need to be taken in order to guard against potential sources of bias. Finally, we cover several methods of analysis and validation appropriate for this kind of data. These steps are illustrated through our creation and exploitation of a new and innovative dataset - the websites of local governments in Indiana and Louisiana. We show that if our methodology is followed appropriately, an association between mayoral partisanship and the content of their cities' websites becomes visible.

>>>>

Government websites are vital for transparency and have become a prominent source of data for automated text analysis in public administration research as well as political science at large. However, extant scholarship lacks common standards and often glosses over the details of how such analyses are conducted. We develop a set of guidelines and procedures to be followed in order to produce valid results. For the acquisition of website data, we cover several scraping methods and difficulties that can arise in the process. Pre-processing is a particularly vital step in text analysis, but when websites are concerned, additional measures need to be taken in order to guard against potential sources of bias. We propose a new method for dealing with the kind of duplicated content that is commonly found in this type of data. Finally, we compare several methods of analysis and validation appropriate in this context. These steps are illustrated through our creation and exploitation of a new and innovative dataset - the websites of local governments in Indiana and Louisiana. We show that if our methodology is followed appropriately, an association between mayoral partisanship and the content of their cities' websites becomes visible.
